\documentclass[12pt,oldfontcommands]{memoir}
\usepackage{cv}

\title{Paul Kilgo}
\date{}

% Footer content
\cfoot{pkilgo@clemson.edu}
\lfoot{Paul Kilgo}
\rfoot{205.210.9536}

\begin{document}
\maketitle
\thispagestyle{fancy}

\section*{Academics}

\begin{itemize}[leftmargin=*]
  \item Ph.D. in Computer Science, Clemson University, 2012--present.
  \begin{itemize}
    \item Dissertation Topic:
          ``Numerical Computation of Feynman Path Integrals for Multiple
            Scattering Physics in Volume Rendering''
    \item Advisor: Jerry Tessendorf, Ph.D.
  \end{itemize}

  \item M.S. in Computer Science, The University of Alabama, 2012.
  \begin{itemize}
    \item Thesis: ``RDIS: A domain model for generalizing the mappings between
                    robotic software frameworks and robotic devices''
    \item Advisor: Monica Anderson, Ph.D.
  \end{itemize}

  \item B.S. in Computer Science and Mathematics, magna cum laude, The
        University of Alabama, 2011.
\end{itemize}

\section*{Research Experience}

Dissertation Research, Clemson University School of Computing, 2014--present.

\begin{itemize}
  \item Investigated methods for numerically computing Feynmath path integrals
        for a formulation of the radiative transport equation.
  \item Benchmarked root-finding algorithms in a path generation and formulated
        an algorithm for asymptotic speedup.
\end{itemize}

Directed Projects, Clemson University School of Computing, Summer 2013.

\begin{itemize}
  \item Developed a node-based, rendering engine-agnostic plug-in for Blender
        for resolution independent volume modeling and grid computation using Python
        and SWIG.
\end{itemize}

Graduate Research Assistant, The University of Alabama Computer Science
Department, Summer 2012.

\begin{itemize}
  \item Developed and implemented a domain model for declarative specification
        of robotic device drivers.
  \item Introduced a visual modeling language for the domain model.
\end{itemize}

Research Assistant, Kilgo Headache Clinic, Summer 2008.

\begin{itemize}
  \item Wrote software using Swing and JDBC used by other research assistants
        for data entry.
  \item Performed data collection and entry for a restrospective study on
        patient retention in private medical practices.
\end{itemize}

Undergraduate Research Assistant, The University of Alabama Center for
Materials for Information Science, 2007.

\begin{itemize}
  \item Performed calibrations on gap separation for a vibrating sample
        magnetometer.
  \item Started an equipment documentation project using MediaWiki.
\end{itemize}

\section*{Teaching Experience}

Graduate Teaching Assistant, Clemson University School of Computing, 2012.

\begin{itemize}
  \item Co-led two lab sections (about 50 students) of CP SC 215: Software
        Development Foundations (Java). Graded projects for three sections (about 75
        students).
\end{itemize}

Graduate Teaching Assistant, The University of Alabama Computer Science
Department, 2011--2012.

\begin{itemize}
  \item Led a recitation session for one section of CS 360: Data Structures and
        Algorithm Analysis (about 30 students).
  \item Graded homework assignments for CS 470 and CS 570: Introduction to
        Computer Algorithms (about 50 students).
  \item Lectured and graded for one section (about 40 students) of CS 250:
        Programming II course (Python).
\end{itemize}

\section*{Professional Experience}

Graduate Lab Assistant, Clemson University School of Computing, 2013--present.

\begin{itemize}
  \item Assisted Systems Programmers in the management of 100+ Linux desktops
        (open lab and research lab) and servers using Puppet and related
        technologies.
  \item Led development for a Django application for arbitrary resource
        management, including VCS repositories and databases (about 100
        registered users). Contributed to several underlying open-source
        libraries dealing heavily with version control systems and SSH key
        management.
  \item Contributed to Django application for Mercurial-based homework and lab
        submissions (1500+ registered users, 35000+ repositories).
  \item Built custom Debian packages, set up custom Apt repositories, and
        managed a Jenkins instance for local development.
\end{itemize}


Student Assistant, The University of Alabama Center for Materials for
Information Science, 2007--2011.

\begin{itemize}
  \item Initiated and managed several Linux-based services including a
        motion-activated surveillance system, a faculty and student web space
        signup system (PHP LAMP with Perl system scripts), and PXE imaging of
        Windows desktops.
  \item Assisted IT Manager in support of 80-100 Windows desktop and
        instrument-attached machines.
  \item Helped maintain two OSCAR Linux clusters.
\end{itemize}

\nocite{*}
\bibliographystyle{plainyr-rev}
\bibliography{cv}

\end{document}
