% Resume for Paul Kilgo

\documentclass[11pt]{simplecv} 
\usepackage{fancyhdr}
\usepackage{url}
\usepackage{fullpage}
\usepackage{pslatex}
\usepackage[numbers]{natbib}

\setlength{\headheight}{12pt} % allow room for 2-line header
\setlength{\headsep}{12pt}  % space between header and text

% Some semantic macros
\newcommand{\stitle}{\textbf}
\newcommand{\sdate}{\textit}
\newcommand{\splace}{\textit}
\newcommand{\email}{\texttt}

%% NO MORE BIBLIOGRAPHY LABELS.
\makeatletter
\def\@biblabel#1{\textbullet \hspace{0.25em}}
\makeatother

%% Rename "References" to "Publications"
\renewcommand{\bibsection}{
  \section{Publications}
}

%% Inputs provided file only if it exists. Otherwise, put some placeholder
%  text.
\newcommand{\inputifexists}[2]{
  \IfFileExists{#1}{\input{#1}}{#2}
}

% Flag for CV mode
\newif\ifcv
\newif\ifprojects
\newif\ifmetadata

%% Comment out for SUPER BRIEF RESUME ACTION.
\cvtrue
\metadatatrue
%\projectstrue

\pagestyle{fancy}     % set pagestyle for document

%% Name in top-right corner. IF CV: also the page number.
\rhead{
  \textit{P. Kilgo}
  \ifcv
    \\ \textit{p. \thepage} 
  \fi
}

\cfoot{\ifmetadata Last update: \today \fi}

\topmargin=-0.5in % start text higher on the page

% Let's have a special URL style, shall we?
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\ttfamily}}}
\makeatother

\urlstyle{leo}

\begin{document}
\thispagestyle{empty} % this page has no header  


\leftheader{
  \inputifexists{inc/address.tex}
}

\rightheader{
  \inputifexists{inc/contact.tex}{}
}

\title{Paul M. Kilgo}

\maketitle

\begin{center}
  \email{pkilgo@clemson.edu}
\end{center}

%% Objective section if one is defined.
\IfFileExists{inc/objective.tex}
  {
    \section{Objective}
    \input{inc/objective.tex}
  }
  {}

%To obtain the New Grad Software Engineer position with Google Inc.

%%%%%%%%%%%%%%%%%%%%
% SECTION: Academics
%%%%%%%%%%%%%%%%%%%%
\section{Academics} 

\begin{topic}

\item[Aug 2012] {
  \stitle{Master of Science}, Computer Science \\
  The University of Alabama, Tuscaloosa, AL \\
}

\item[May 2011] {
  \stitle{Bachelor of Science}, Computer Science, Mathematics \\
  The University of Alabama, Tuscaloosa, AL \hspace{0.2in} GPA 3.815
}

\end{topic}
  
%%%%%%%%%%%%%%%%%%%%
% SECTION: Work Experience
%%%%%%%%%%%%%%%%%%%%
\section{Work Experience} 

\begin{topic}

\item[Aug 2012--present] {
  \stitle{Graduate Assistant} \\
  \splace{School of Computing} \\
  Clemson University, Clemson, SC

\ifcv
  \begin{itemize}
    \item Maintained and developed software for School of Computing Linux systems
    \item Led lab and graded for an intermediate programming course.
  \end{itemize}
\fi
}

\item[Aug 2011--Jun 2012] {
  \stitle{Graduate Assistant} \\
  \splace{Computer Science Department} \\
  The University of Alabama, Tuscaloosa, AL

\ifcv
  \begin{itemize}
    \item Research in robotics software/middleware
    \item Lectured and graded for undergraduate data structures/algorithms course.
    \item Graded for undergraduate/graduate algorithms course.
    \item Lectured and graded for Programming II course.
  \end{itemize}
\fi
}

\item[Summer 2010] {
	\stitle{Student Volunteer} \\
	\splace{The Good Samaritan Clinic} \\
	Northport, AL

\ifcv
	\begin{itemize}
		\item Performed triage procedures for incoming patients.
	\end{itemize}
\fi
}

\item [Fall 2009] {
	\stitle{Project-Based Intern} \\
	\splace{Creative Campus} \\
	The University of Alabama, Tuscaloosa, AL
	
\ifcv
	\begin{itemize}
		\item Organized weeklong game development workshop.
	\end{itemize}
\fi
}


\item[Summer 2008] {  
  \stitle{Programmer, Researcher, DBA} \\
  \splace{Kilgo Headache Clinic} \\
  Northport, AL

\ifcv
  \begin{itemize}
    \item Managed MySQL database for research data.
    \item Created Java-based data entry client.
    \item Performed data entry.
  \end{itemize}
\fi
}

\item[Aug 2007--Aug 2011] {
  \stitle{Student IT Assistant} \\
  \splace{Center for Materials for Information Technology} \\
  The University of Alabama, Tuscaloosa, AL

\ifcv
  \begin{itemize}
    \item Managed Linux-based services.
    \item Created software solutions for IT problems.
    \item Improved many processes.
  \end{itemize}
\fi
}

\item[Summer 2007] {
  \stitle{Student Research Assistant} \\
  \splace{Center for Materials for Information Technology}  \\
  The University of Alabama, Tuscaloosa, AL

\ifcv
  \begin{itemize}
    \item Conducted research in magnetics.
    \item Created equipment documentation project.
  \end{itemize}
\fi
}

\item[Summer 2006] {
	\stitle{Web Designer} \\
	\splace{Neurology Clinic, P.C.} \\
	Northport, AL
}

\ifcv
	\item[Summer 2004] {
		\stitle{Intern} \\
		\splace{Tuscom Computer Solutions} \\
		Tuscaloosa, AL
	}
\fi

\end{topic}


\section{Skills}

\begin{topic}

\item[Proficiency] {
  Java, C++, Python, Shell scripting
}

\item[Familiarity] {
  C, C\#, PHP
}

\item[Development frameworks and platforms] {
  Linux, Windows, Android, OpenGL, SDL
}

\end{topic}

%% This section may be interesting for work-related purposes but maybe 
\ifprojects
  \section{Projects} 

  \begin{topic}

  \item [Rainwave] {
    Created an Android client for Rainwave, an online radio station where users can vote for, request, and
    rate the music which plays. Also, conducted a user study on the client for a Human-Computer Interaction
    course to measure improvements made to the interface.
    
    \url{http://github.com/OEP/rainwave-android}  \\
    \url{http://rainwave.cc/}
  }

  \item [Bamalab] {
    Recreated the Bamalab software using F/OSS technologies. Bamalab is a software package created
    by a UA professor used to teach circuits to freshmen.
    
    \url{http://bamalab.googlecode.com}
  }

  \item [Bama Mobile Registration for Android] {
    Software engineering class project -- a prototype for an Android class registration system for
    the University.
    
    \url{http://bmr-android.googlecode.com/}
  }

  \item[JMingle] {
    A social game for J2ME. Nearby Bluetooth devices are represented as NPC's which the
    player can interact with.
    
    \url{http://jmingle.googlecode.com/}
  }

  \end{topic}
\fi


\section{Memberships} 

\begin{topic}

\item[2009--2012] {
  UA Student Chapter of the Association for Computing Machinery
  
  Served as publicity chair and webmaster for a year.
}

\end{topic}

\section{Academic Honors} 
\begin{topic}
  \item [2012] { ACM Outstanding Graduate Student, The University of Alabama }
  \item [2010] { ACM Outstanding Undergraduate, The University of Alabama }
  \item [2009] { \textit{Upsilon Pi Epsilon} National Honor Society }
  \item [2009] { Outstanding Junior in Computer Science, The University of Alabama }
\end{topic}

\section{Conferences}
\begin{topic}
  \item [2012] { 
    \textit{Presented},
    IEEE International Conference on Robotics and Automation (ICRA)
  }
  \item [2012] { 
    \textit{Presented},
    Association for Computing Machinery Southeastern Conference (ACMSE)
  }
\end{topic}

\section{Peer Review}
\begin{topic}
  \item [2013] { 
    Journal of Software Engineering for Robotics (JOSER)
  }
  \item [2012] { 
    IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)
  }
\end{topic}

%% Prints the bibliography
\nocite{*}
\bibliographystyle{plainyr-rev}
\bibliography{cv}

\end{document}
