Dissertation Research, Clemson University School of Computing, 2014--present.

\begin{itemize}
  \item Investigated methods for numerically computing Feynman path integrals
        for a formulation of the radiative transport equation.
  \item Benchmarked root-finding algorithms in a path generation algorithm and
        formulated an algorithm for asymptotic speedup.
\end{itemize}

Directed Projects, Clemson University School of Computing, Summer 2013.

\begin{itemize}
  \item Developed a node-based, rendering engine-agnostic plug-in for Blender
        for resolution independent volume modeling and grid computation using
        Python and SWIG.
\end{itemize}

Graduate Research Assistant, The University of Alabama Computer Science
Department, Summer 2012.

\begin{itemize}
  \item Developed and implemented a domain model for declarative specification
        of robotic device drivers.
  \item Introduced a visual modeling language for the domain model.
\end{itemize}

Research Assistant, Kilgo Headache Clinic, Summer 2008.

\begin{itemize}
  \item Wrote software using Swing and JDBC used by other research assistants
        for data entry.
  \item Performed data collection and entry for a retrospective study on
        patient retention in private medical practices.
\end{itemize}

Undergraduate Research Assistant, The University of Alabama Center for
Materials for Information Technology, 2007.

\begin{itemize}
  \item Performed calibrations on gap separation for a vibrating sample
        magnetometer.
  \item Started an equipment documentation project using MediaWiki.
\end{itemize}

